\documentclass{article}
\usepackage[margin=1in]{geometry}
% \usepackage{hyperref}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\Huge\textbf{Asif Ahmad}}\\[8pt]
    \textbf{Lecturer @ \href{https://giki.edu.pk/personnel/19086/}{GIK Institute} 
    % \& Co-founder @ \href{https://neuralinternet.ai/}{Neural Internet}
    }
    \\
    % $\diamond$ 
    \href{www.asifahmad.net}{www.asifahmad.net} $\diamond$ \href{mailto:asifahmedmaths@gmail.com}{asifahmedmaths@gmail.com} $\diamond$ \href{mailto:asif.ahmad@giki.edu.pk}{asif.ahmad@giki.edu.pk}
\end{center}

\vspace{3mm}

\section*{\textbf{Education}}
% \hrule\vspace{4pt}
\begin{itemize}
    \item \textbf{University of Engineering \& Technology Peshawar, Pakistan} \hfill Mar. 2018 - Apr. 2020\\
    % {\tiny Master of Science (18-Year) in Applied Mathematics}
    \textit{Master of Science (18-Year) in Applied Mathematics} \hfill \textit{ Supervisor: Dr. Noor Badshah, Ph.D (UK)}\\ 
    Thesis Title: \textbf{Neural Network for Segmentation of Medical Images}\\
    GPA: 3.78/4.0

    \item \textbf{University of Peshawar (UOP), Pakistan} \hfill Nov. 2014 - Mar. 2017\\
    \textit{Master of Science (16-Year) in Mathematics}\\ Grade: A

    \item \textbf{Stanford University (Coursera)} \hfill Completed Feb. 2022\\
    Machine Learning

    \item \textbf{NVIDIA Deep Learning Institute} \hfill Completed Aug. 2019\\
    Fundamentals of Deep Learning for Computer Vision
\end{itemize}
% \hrule

\section*{\textbf{Work Experience}}
% \rule{\textwidth}{0.5pt}
\begin{itemize}


    \item \textbf{Lecturer}, GIK Institute, Pakistan \hfill Feb. 2022 - present\\
    \text{I have been teaching the following undergraduate courses:} 
    \begin{itemize}
    \item Machine Learning (ES 442) \hfill Fall 2025
    \item Calculus I (MT 101) \hfill Fall 2023, 2024, 2025
    \item Advanced Linear Algebra (ES 205) \hfill Spring 2025
    \item Complex Variables \& Transforms (MT 203) \hfill Fall 2024
    \item Probability \& Statistics (ES 111) \hfill Spring 2024
    \item Differential Equations \& Linear Algebra-I (MT 102/202) \hfill S. 2023, F. 2022
    \item Engineering Statistics (ES 202) \hfill Spring 2022 \\

    \end{itemize}
    
    Besides teaching, I am co-ordinator of the Learning Management System (LMS) of the Faculty of Engineering Science, GIK Institute.

    \item \textbf{Co-founder and ML Team Lead}, Neural Internet, USA \hfill Sep. 2022 - May 2025
    \begin{itemize}
        \item Led a Machine Learning team focused on developing decentralized applications leveraging various subnets within the Bittensor network.
        \item Provided technical guidance and collaborated with the development team on the Compute Subnet (SN-27), contributing technical insights and suggesting improvements.
        \item Contributed to the maintenance and operational stability of network validators on the Bittensor network.
        \item Collaborating with the Bittensor community to advance decentralized AI capabilities
    \end{itemize}

    % \item \textbf{Co-founder and Technical Lead}, Neural Internet, USA \hfill Sep. 2022 - May 2025
    % \begin{itemize}
    %     \item Spearheading the development of the Compute Subnet (SN-27), a decentralized computing platform on the Bittensor network
    %     \item Leading the validators' maintenance team
    %     \item Collaborating with the Bittensor community to advance decentralized AI capabilities
    % \end{itemize}

    \item \textbf{Mathematics Lecturer}, CECOS University, Pakistan \hfill Mar. 2020 - Jan. 2022

    \item \textbf{Mathematics Lecturer (Visiting)}, CECOS University, Pakistan \hfill Oct. 2019 - Mar. 2020

    \item \textbf{Research Assistant}, UET Peshawar, Pakistan \hfill Feb. 2019 - Feb. 2020

    \item \textbf{Mathematics Lecturer}, Govt. Degree College Chitral, Pakistan \hfill Aug. 2017 - Aug. 2018
\end{itemize}

\section*{\textbf{Research Experience}}
\vspace{1mm}
\hspace{4mm} \textbf{Neural Network for Segmentation of Medical Images}\hfill \textit{Masters' Thesis Work} \\
Developed and trained a deep neural network for the segmentation of medical images during masters' degree research. In addition to my thesis, I also collaborated with other graduate students to explore Activate Contour Models integration in neural networks and their application in medical images processing. \\

\textbf{Skin Cancer Detection with Deep Neural Networks and Vision Transformers}\\
We used transfer learning for finetuning different convolutional deep neural networks and vision transformers for classification of cancerous skin images.\\

\textbf{Solving Partial Differential Equations Using Physics Informed Neural Networks (PINNs)}\\
Worked on developing and training a physics-informed neural network for solving PDEs with a graduate student at GIK Institute as his co-supervisor. We enhanced PINN Performance Through Lie Symmetry Group, and solved Newell-Whitehead-Segel, Allen-Cahn, and Burgers' Equations.\\

\textbf{Careem Captain Fraud Detection} \hfill \textit{CO-PI}\\
In this project with Careem, a well known ride-hailing services provider company in the Middle East region, we explored different data processing techniques and machine learning algorithms to automate their Captain (driver) fraud detection. \\

\textbf{Neural Network for Detection of Hidden Explosives and Narcotics Using Multi-pulse NQR} \\
In this work, we developed a deep neural network-based approach for the rapid detection of hidden explosives and narcotics using Multipulse Nuclear Quadrupole Resonance (NQR).\\

\textbf{AI-based Service Request Analysis and Rate Limiting for Fair and Efficient Use of NADRA Resouce} \hfill \textit{PI} \\
I am leading this project from the National Database and Registration Authority (NADRA) titled "AI-based Service Request Analysis and Rate Limiting for Fair and Efficient Use of NADRA Resouce", where the goal is to automate anomaly detection followed by rate limiting of requests for different services in NADRA. \\


\textbf{Mathematics for Machine Learning} \hfill \textit{Work in Progress}\\
We are compiling a book on \textbf{Mathematics for Machine Learning}, covering fundamental concepts in Probability, Statistics, Calculus, and Linear Algebra, accompanied by hands-on practice examples implemented in Python.

\section*{\textbf{Publications}}
% \hrule
\vspace{3pt}
\subsection*{Book Chapters}
\begin{itemize}
    \item Muniba Ashfaq, \textbf{Asif Ahmad}, \textit{Skin cancer classification with convolutional deep neural networks and vision transformers using transfer learning}, Springer Nature, 2024.
\end{itemize}

\subsection*{Journal Articles}
\begin{itemize}
    \item Noor Badshah, \textbf{Asif Ahmad}, \textit{ResBCU-Net: Deep learning approach for segmentation of skin images}, Biomedical Signal Processing and Control, Elsevier, 2022.
    \item \textbf{Asif Ahmad}, Noor Badshah, Mahmood Hassan, Kamboh Well, \textit{A Modified Memory-Efficient U-Net for Segmentation of Polyps}, International Journal of Engineering Works, 2021.
    % \item Ali Haider Shah, Naveed Razzaq Butt, \textbf{Asif Ahmad}, Muhammad Omar bin Saeed, \textit{Enhancing PINN Performance Through Lie Symmetry Group}, under review, 2024.
    % \item Ali Haider Shah, Naveed Razzaq Butt, \textbf{Asif Ahmad}, Muhammad Omar bin Saeed, \textit{Solving Newell-Whitehead-Segel and Allen-Cahn Equations Employing Physics-Informed Neural Networks: A Comparative Analysis with Spline Methods}, under review, 2024.
\end{itemize}

\subsection*{Conference Papers}
\begin{itemize}
    \item Mehreen Fida, Noor Badshah, \textbf{Asif Ahmad}, Abdul Hafeez, Arif Ullah, Yalin Zheng, \textit{Neural Network Integrated with Active Contour Model for Segmentation of Medical Images}, Ahi Evran International Conference on Scientific Research, 30 November -1-2 December, 2021.
    \item Arif Ullh, Noor Badshah, \textbf{Asif Ahmad}, Abdul Hafeez, Mehreen Fida, \textit{Deep Learning Approach for Segmentation of Medical Images}, Ahi Evran International Conference on Scientific Research, 30 November -1-2 December, 2021.
\end{itemize}

\subsection*{Preprints}
\begin{itemize}
    \item \textbf{Asif Ahmad}, Naveed R Butt, Babar Zaman,  \textit{Deep Neural Network Based Accurate and Fast Detection of Hidden Explosives and Narcotics Using Multi-Pulse Nuclear Quadrupole Resonance}, Available at SSRN 4948911.
    \item Ali Haider Shah, Naveed Razzaq Butt, \textbf{Asif Ahmad}, Muhammad Omar bin Saeed, \textit{Enhancing PINN Performance Through Lie Symmetry Group}, arXiv.org e-Print archive, 2025.
    \item Ali Haider Shah, Naveed Razzaq Butt, \textbf{Asif Ahmad}, Muhammad Omar bin Saeed, \textit{Solving Newell-Whitehead-Segel and Allen-Cahn Equations Employing Physics-Informed Neural Networks: A Comparative Analysis with Spline Methods}, arXiv.org e-Print archive, 2025.


\end{itemize}

\section*{\textbf{Supervision of Graduate Students}}
% \hrule
\vspace{3pt}
\begin{itemize}
    \item Co-supervised MS thesis titled \textit{Solving PDEs Using Improved Physics-Informed Neural Networks (PINNs) and Lie Symmetry} of Ali Haider (Reg. \# ES-2264), at GIK Institute of Engineering Sciences \& Technology Topi, Pakistan.
\end{itemize}

\section*{\textbf{Conferences/Workshops}}
\begin{itemize}
    \item 5-Day Training Workshop on \textbf{Teaching Statistics \& ML using Python} \hfill \textit{Instructor} \hfill Jan. 2023 
    \item 1st Intl. Conference on Science, Engineering \& Technology \textbf{(ICSET-21)} \hfill \textit{Presenter} \hfill Mar. 2021
    \item National Conf. on Mathematical Sciences in Engrg. Applications \textbf{(NCMSEA)} \hfill \textit{Organizer} \hfill Apr. 2018

\end{itemize}
% \section*{Master's Thesis}
% % \hrule
% \vspace{5pt}
% Neural Network for Segmentation of Medical Images

\section*{\textbf{Honours and Awards}}
\begin{itemize}
    \item MS Studentship at National Center of Big Data \& Cloud Computing (NCBC), UET, 2019.
\end{itemize}


\section*{\textbf{Computer Skills}}
% \hrule
\vspace{3pt}
\textbf{Programming:} Python, MATLAB\\ 
\textbf{Paper Writing:} LaTeX, MS Word

% \section*{\textbf{Computer Skills}}
% % \hrule
% \vspace{3pt}
% \textbf{Programming:} Python (Pandas, Matplotlib, Seaborn, PyTorch, TensorFlow), MATLAB\\ 
% \textbf{Paper Writing:} LaTeX, MS Word

% \section*{Language Skills}
% % \hrule
% \vspace{5pt}
% Khowar (Mother Tongue), English, Urdu, Pashto


\section*{\textbf{References}} 
\vspace{3pt} 
\begin{itemize} \item \textbf{Dr. Naveed Razzaq Butt, Ph.D (LU, Sweden)}, \hfill Former Dean FES, GIK Institute\\ \texttt{email: nnaveed.butt@sse.habib.edu.pk}, Ph: +92 3067050474 \item \textbf{Dr. Noor Badshah, Ph.D (University of Liverpool, UK)}, \hfill Professor, UET Peshawar\\ \texttt{email: noorbadshah@uetpeshawar.edu.pk}, Ph: +92 3447552462 \item \textbf{Dr. Siraj Ul haq, Ph.D (University of Liverpool, UK)}, \hfill Professor, GIK Institute\\ \texttt{email: siraj@giki.edu.pk}, Ph: +92 3349334599 \item \textbf{Dr. Omer Bin Saeed, Ph.D (KFUPM, Saudi Arabia)}, \hfill Associate Professor, GIK Institute\\ \texttt{email: omer.saeed@giki.edu.pk}, Ph: +92 3345079401 
\end{itemize}


\end{document}
